Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Abstract, Figure 1

\begin{abstract} 
    Massive galaxies display extended light profiles that can reach out to several 
    hundreds of kilo parsecs. 
    These stellar halos are a key fossil record of galaxy assembly history. Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    the $i$-band), we present a systematic study of the stellar halos of  a sample of more than $7000$ galaxies at $0.3 < z < 0.5$. 
Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) survey, which reaches ${\sim}4$ magnitudes fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
    without resorting to stacking. Shallow images and/or over-simplified parametric models cannot capture the extended stellar halo and result in underestimated stellar masses.
    Our extended profiles reveal a number of mass-dependent trends. The outer parts of our galaxies have higher ellipticity, and this ellipticity increases with stellar mass, but we find no difference in color gradients with mass. As in previous work, we see a clear trend towards more extended outer profiles in more massive galaxies. Thus, when this extended light is not properly accounted for, the stellar mass function is systematically underestimated at the highest masses. Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging. We provide surface mass surface mass density profiles in a convenient tabulated format to facilitate comparisons with predictions from numerical simulations of galaxy formation.\end{abstract}

%massive central galaxies display surface mass density profiles that are not 
%    self-similar, with the outer-slope becoming shallower and the fraction of mass 
%    in the outskirt increasing with total stellar mass (xxxxxxxxx).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the depth and imaging quality of SDSS and the HSC wide 
            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
            This added depth is critical in order map the outskirts of ETGs out to 
            large radii.
\rachel{Should replace the quote marks with arcsec symbols in the scale on these plots.}
}
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

  % Personal 
  SH thanks F.S.Liu for sharing the data from his work.

@@

>>>>

\begin{abstract} 
    Massive galaxies display extended light profiles that can reach out to several 
    hundreds of kilo parsecs. 
    These stellar halos are a key fossil record of galaxy assembly history. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which reaches ${\sim}4$ magnitudes 
    fainter than SDSS and enables us to directly trace mass profiles to 100 kpc 
    without resorting to stacking. 
    Shallow images and/or over-simplified parametric models cannot capture the extended 
    stellar halo and result in underestimated stellar masses.
    Our extended profiles reveal a number of mass-dependent trends. 
    The outer parts of our galaxies have higher ellipticity, and this ellipticity increases 
    with stellar mass, but we find no difference in color gradients with mass. 
    As in previous work, we see a clear trend towards more extended outer profiles 
    in more massive galaxies. 
    Thus, when this extended light is not properly accounted for, the stellar mass 
    function is systematically underestimated at the highest masses.
    Our results are broadly consistent with the two phase formation scenario of massive 
    galaxies in which outer envelopes are built up at late times from minor merging. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.
\end{abstract}

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the depth and imaging quality of SDSS and the HSC wide 
            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
            This added depth is critical in order map the outskirts of ETGs out to 
            large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

  % Personal 
  The authors thank Frank van~den~Bosch for insightful discussions.
  SH thanks F.S.Liu for sharing the data from his work.

@@

  % KITP
  This research was supported in part by the National Science Foundation under Grant 
  No. NSF PHY11-25915.
